The \dealii Library, Version 9.7

### 2025-07-14 9.7/paper.tex
Add some text for the orientation changes.

The 9.7 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_5_2_and_9_6_0.html}
     {around 40 incompatible changes};
     \todo{Update link and number}
see \cite{changes97}. Many of these
incompatibilities change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
are more broadly visible:
\begin{itemize}
  \item \todo[inline]{Update}
\end{itemize}

>>>>

The 9.7 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_5_2_and_9_6_0.html}
     {around 40 incompatible changes};
     \todo{Update link and number}
see \cite{changes97}. Many of these
incompatibilities change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
are more broadly visible:
\begin{itemize}
  \item \todo[inline]{Update}
  \item We have continued to unify the various implementations of object
    orientations in the library. While the three booleans orientation, rotation,
    and flip have maintained their original meanings (i.e., they have default
    values of \texttt{true}, \texttt{false}, and \texttt{false}), the default
    value of the combined orientation (available via
    \texttt{TriaAccessor::combined\_face\_orientation()} and
    \texttt{TriaAccessor::line\_orientation()}) is now $0$ rather than $1$. In
    addition, the return type of these functions is now
    \texttt{types::geometric\_orientation}, which is a \texttt{typedef} for an
    8-bit integral type.
\end{itemize}
